---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# HTLR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Build Status](https://travis-ci.org/longhaiSK/HTLR.svg?branch=dev)](https://travis-ci.org/longhaiSK/HTLR)
<!-- badges: end -->

`HTLR` performs classification and feature selection by fitting Baeysian polychotomous (multiclass, multinomial) logistic regression models based on heavy-tailed priors with small degree freedom. This package is suitable for classification with high-dimensional features, such as gene expression profiles. Heavy-tailed priors can impose stronger shrinkage (compared to Guassian and Laplace priors) to the coefficients associated with a large number of useless features, but still allow coefficients of a small number of useful features to stand out without punishment. It can also automatically make selection within a large number of correlated features. The posterior of coefficients and hyperparameters is sampled with resitricted Gibbs sampling for leveraging high-dimensionality and Hamiltonian Monte Carlo for handling high-correlations among coefficients. 

This site focuses mainly on illustrating the usage and syntax of `HTLR`. For more details on the algorithm, see the original article: <[DOI:10.1080/00949655.2018.1490418](https://www.tandfonline.com/doi/full/10.1080/00949655.2018.1490418)>
([PDF](https://arxiv.org/pdf/1405.3319.pdf)).

## Installation

~~You can install the released version of HTLR from [CRAN](https://CRAN.R-project.org) with:~~

``` r
install.packages("HTLR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("longhaiSK/HTLR")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(HTLR)
## basic example code
```

This page is under construction.
